How Well do we Teach Cybersecurity?\\(Abstract 20 January, Paper 27th)

### 2018-12-20 ITiCSE2019.tex
More fixes

\author{Alastair Irons}
\orcid{}
\affiliation{%
  \institution{Sunderland University}
  \streetaddress{}
  \city{Sunderland} 
  \country{United Kingdom}
}
\email{@alastair.irons@sunderland.ac.uk}

@@

Specialist curricula abound: a recent one is \cite{ACM2017b}. However, given the shortage of specialists, in practice a good generalist with some CYberSecurity expertise can often get a ``specialist''.
\section{Policy Context}

>>>>

\author{Alastair Irons}
\orcid{}
\affiliation{%
  \institution{Sunderland University}
  \streetaddress{}
  \city{Sunderland} 
  \country{United Kingdom}
}
\email{alastair.irons@sunderland.ac.uk}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist''.
\subsection{Research Questions}
\begin{enumerate}
\item The person in teh street --- probably not.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\section{Policy Context}
